A Study of INC Runs in Sequence

### 2018-12-15 pt_characterization/protocol/intermediate_data/paper.tex
Slightly modified

\section{Description}
In this document we discuss characteristics of INC runs in sequence.

There are two big subjects included in the document.
Specifically, the first subject relates running a series of INCs in a batch, pausing the run, and then resuming 
the run, rather than repeating the same INC multiple times. 
That is, INC1, ..., INC16384 are consecutively run as a batch, and 
then the entire batch run sleeps for an hour, and then 
another batch run of INC1, ..., INC16384 begins, stops, and resumes, and so forth.

The second subject concerns breaking up 
a whole run of 1000 samples into 200 samples, thereby yielding five different histograms.

@@

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|p{4cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period\\ \hline
{\tt sodb9} &  INC16 & Each run with 1,000 samples & 2017-03-02 $\sim$ 2017-03-07\\ \hline
{\tt sodb9} &  INC1~INC16384 & One run in which each INC has 30 samples & 2018-11-17 $\sim$ 2018-12-02\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:exp_notes}}
\end{table}

@@

\begin{figure}[htp!]
	\centering
	\subfigure[PT frequency on INC16 with the first 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_1.eps}
		\label{fig:inc16-1}
	}
	\subfigure[PT frequency on INC16 with the next 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_2.eps}
		\label{fig:inc16-2}
	}
	\subfigure[PT frequency on INC16 with the next 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_3.eps}
		\label{fig:inc16-3}
	}
	\subfigure[PT frequency on INC16 with the next 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_4.eps}
		\label{fig:inc16-4}
	}
	\caption{PT Histograms of INC16-1$~$INC16-4~\label{fig:inc16_hist1}}
\end{figure}

>>>>

\section{Description}
In this document we study the characteristics of INC runs that are executed in sequence.

Broadly speaking, there are two {\em subjects} included in the document.
The first subject, which is discussed in Section 1, involves {\it i}) running as a {\em batch} a series of INCs with increasing task length and {\it ii}) pausing the batch run. This entire batch run including the pause continues until the specified number of iterations, say 30, is specified. More specifically, INC1, ..., INC16384 are consecutively run as a batch, and 
then the entire batch run sleeps for an hour, and then another batch run begins and stops, and again the new batch run resumes. This type of batch run is distinct from repeatedly running the same INC with a single task length.

The second subject, which is discussed in Section 2, iconcerns dividing 
a single run of 1000 samples on INC16 into five consecutive subruns of 200 samples.  
For each subrun, we examine their respective PT (program time) histograms 
and see if the histograms look similar to each other.

@@

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|p{4cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period\\ \hline
{\tt sodb9} &  INC16 & Each run with 1,000 samples & 2017-03-02 $\sim$ 2017-03-07\\ \hline
{\tt sodb9} &  INC1$\sim$INC16384 & One run in which each INC has 30 samples & 2018-11-17 $\sim$ 2018-12-02\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:exp_notes}}
\end{table}

@@

\begin{figure}[htp!]
	\centering
	\subfigure[PT frequency on INC16 with the first 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_1.eps}
		\label{fig:inc16-1}
	}
	\subfigure[PT frequency on INC16 with the next 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_2.eps}
		\label{fig:inc16-2}
	}
	\subfigure[PT frequency on INC16 with the next 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_3.eps}
		\label{fig:inc16-3}
	}
	\subfigure[PT frequency on INC16 with the next 200 samples on {\tt sodb9}]{
		\includegraphics[scale=0.43]{16_sec_pt_hist0_4.eps}
		\label{fig:inc16-4}
	}
	\caption{PT Histograms of INC16-1$\sim$INC16-4~\label{fig:inc16_hist1}}
\end{figure}
